---
title: "Lab 05 - Make a Shiny app from a Rmd file"
subtitle: "interactive graphs"
output: 
  tufte::tufte_html:
    css: ../lab.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes
---

In this lab we will create a simple Shiny app from an R markdown document in order to create interactive plots.

# Learning goals

-   Practice making Shiny apps
-   Understand the value of interactive plots

# Getting started

Go to the course GitHub organization and locate your lab repo, clone it in RStudio and open the R Markdown document.
Knit the document to make sure it compiles without errors.

## Warm up

Before we introduce the data, let's warm up with some simple exercises.
Update the YAML of your R Markdown file with your information, knit, commit, and push your changes.
Make sure to commit with a meaningful commit message.
Then, go to your repo on GitHub and confirm that your changes are visible in your Rmd **and** md files.
If anything is missing, commit and push again.

## Packages

We'll use the **tidyverse** package for data wrangling and visualisation.
These packages are already installed for you.
You can load them by running the following in your Console:

```{r message = FALSE}
library(tidyverse) 
```

## Rmd R markdown file

The R Markdown file describes an experiment where some data was collected for running neural networks under different conditions.
In the last bar chart you can see the FPS (Frames Per Second) or running the neural network for different sized models (YOLO X Large through YOLO X Tiny).

We want to make an Shiny app that allows you to investigate the data interactively.

🧶 ✅ ⬆️ Knit, *commit, and push your changes to GitHub with an appropriate commit message. Make sure to commit and push all changed files so that your Git pane is cleared up afterwards.* \# Exercises

## Exercises

### Exercise 1.

To start with your Shiny app, open the file called inferenceApp.R.
Rstudio cloud will ask you to load the necessary packages - go ahead and do that, then click 'Run App'.
You should see a mostly empty app appear in a separate window.

### Exercise 2.

At the start of your server code add your code that reads in the data.
You can copy / paste the code right out of your Rmd file.
You'll also have to include the 'janitor' package at the top of the file (again can get this from the Rmd file).

Now add your plot

-   add the line in the ui portion in the mainPanel. the output is plotOutput(outputId = "theplot")

```{r, eval=FALSE}
    mainPanel(
      # add your plot here
      )
```

-   Copy the plot from the Rmd file and put it into the renderPlot expression

```{r, eval=FALSE}
  output$theplot <- renderPlot({
  # add your plot here.  Make sure to reference your input variables
  })
```

Now run the App, and you should see the plot appear.
But there aren't any controls yet to select different parameters.

### Exercise 3.

Let's add a sidebar selection to select between CPU and GPU.
Under sidebarLayout, add an input selection,

```{r, eval=FALSE}
selectInput(inputId = "GPU", 
            label = "GPU selection", 
            choices = c("GPU","CPU"), 
            selected = "CPU")
```

Next, the inputId of your selectInput needs to be mapped to your plot.
In order to do that, in your plot code, you have to reference the inputId - replace theGPUfilter in the filter statement with input\$GPU.

Now, when you run the App, you should be able to update the plot to see data for just CPU or just GPU.
But notice that the title doesn't update.
Update the labs() section to reflect the selected input.

```{r, eval=FALSE}
      labs(title = input$GPU)
```

### Exercise 4.

Add a selection for network to your graph so you can slice by this variable.
Add another selectInput to select network factors.
Add the below code to the sidebarPanel in your ui section of your app.
Make sure you correct for any syntax errors.

```{r, eval=FALSE}
      selectInput(inputId = "network", label = "network type",
                  choices = c("none","wired","wireless"),
                  selected = "none")
```

Once you have the selectInput implemented, you have to update your graph code to use the input.

```{r, eval=FALSE}
# Replace theNetworkFilter with input$network in the filter statement

```

Re-run your app.
You should now have a functional app that you can select different plotting variables with.

### Exercise 5.

One last thing you can do is to allow multiselection of the network variable - to do this add multiple = TRUE to the selectInput statement for the inputId = "network"

Re-run the app.

### Exercise 6.

You can publish your app to shiny.io so that the world can see your work.
We will go over how to do this in class.
